### 2004-12-16 classes/algorithms/final.tex
final algo exam

Then we simply use DAG-SP to compute the shortest path from the start
to then end vertex.  This takes time $O(V+E) = O(n)$.  This shortest
path will have weight $\sigma_{k=i}^j -x_k$ for all the $v_{x_k}$ that
it passes through.  But minimizing this sum corresponds exactly to
maximizing  $\sigma_{k=i}^j x_k$.  Therefore, the shortest path is the
sequence of numbers that maximizes $S(i,j)$.

@@

>>>>

Then we simply use DAG-SP to compute the shortest path from the start
to then end vertex.  This takes time $O(V+E) = O(n)$.  This shortest
path will have weight $\sigma_{k=i}^j -x_k$ for all the $v_{x_k}$ that
it passes through.  But minimizing this sum corresponds exactly to
maximizing  $\sigma_{k=i}^j x_k$.  Therefore, the shortest path is the
sequence of numbers that maximizes $S(i,j)$. \qed

@@

If edge $e$ does participate in the maximal flow, then consider the
flow network for graph $G$ given by making the capacity of each edge
the quanity of flow on that edge in $f$. Compute some path from the
source to the sink using edge $e$.  This can be done in time $O(V+E)$
by simply searching forwards from the ending vertex of $e$, and
backwards from the starting vertex of $e$.  Then add the flow on this
path to the residual network left after computing the original flow
$f$.  Then, remove edge $e$ from this augmented flow network.  If
there is still a path from the source to the sink, then it is possible
to route around the deletion, and the new flow is the original flow
with the first augmenting path removed, and the new augmenting path
added.  Otherwise, the new flow is simply the old flow with the
augmenting path removed, and the new flow has size $|f|-1$.
\qed
